Transfer report

### 2018-10-20 Report/descriptives.Rmd
Moves functions to helpers, creates new report part

## Female/male

# Report
A total of `r nrow(df_participants)` (M = `r round(mean(df_participants$age, na.rm=T),1)`, SD = `r round(sd(df_participants$age, na.rm=T), 1)`) undergraduate students at UC Davis particiapted in the study in exchange for a study credit. Each students was randomly assigned a condition and a randomised set of goals. `r sum(finished$no)` participants didn't finish due to motion sickness and `r sum(is_ok$no)` were removed due to a technical failure of the real world tracking systen. Only `r finished[finished$condition == "vr-real","percent"] * 100` percent the students being able to finish VR to Real world condition.

@@

```{r}
kable(walk_all %>% group_by(type, exp_block_id) %>% summarize(mean_dist = mean(distance, na.rm=T), mean_time = mean(time, na.rm=T)))
```

>>>>

## Female/male
```{r, echo=F}
kable(df_participants %>% filter(finished=="yes") %>% group_by(condition, sex) %>% count)
```

# Report
A total of `r sum(overview$is_ok == "yes", na.rm=T)` (M = `r round(mean(df_participants[df_participants$finished == "yes",]$age, na.rm=T),1)`, SD = `r round(sd(df_participants[df_participants$finished == "yes",]$age, na.rm=T), 1)`) undergraduate students at UC Davis particiapted in the study in exchange for a study credit. Each students was randomly assigned a condition and a randomised set of goals. `r sum(finished$no)` participants didn't finish due to motion sickness and `r sum(is_ok$no)` were removed due to a technical failure of the real world tracking systen. Only `r finished[finished$condition == "vr-real","percent"] * 100` percent the students being able to finish VR to Real world condition.

@@

```{r}
df_desc <- walk_all %>% group_by(type, exp_block_id) %>% summarize(mean_dist = mean(distance, na.rm=T), mean_time = mean(time, na.rm=T))
ggplot(df_desc, aes(exp_block_id, mean_dist, fill=type)) + geom_bar(stat="identity", position = "dodge")
ggplot(df_desc, aes(exp_block_id, mean_time, fill=type)) + geom_bar(stat="identity", position = "dodge")
```

### 2018-10-20 Report/paper-story.Rmd
new reports
Moves functions to helpers, creates new report part

---
title: "Transfer report"
author: "Lukáš Hejtmánek"
date: "9 August 2018"
output: html_document
---

@@

```{r, echo=F}
df_dist <- block_t_test(sub_walk_all, 1, 4,"min_norm_distance")[,c(1,4)]
df_error <- block_t_test(sub_walk_all, 1, 4,"errors")[,c(1,4)]
df14 <- merge(df_dist, df_error, by = "learning.condition")
colnames(df14) <- c("learning condition", "p-value distance improvement", "p-value errors improvement")
kable(df14, caption="Paired T test comparing infividual performance improvement from block 1-4 in different conditions")
```

>>>>

---
title: "Transfer report"
author: "Lukáš Hejtmánek"
date: "9 August 2018"
output: github_document
---

@@

```{r, echo=F}
df_dist <- block_t_test(sub_walk_all, 1, 4,"min_norm_distance")[,c(1,4)]
df_error <- block_t_test(sub_walk_all, 1, 4,"errors")[,c(1,4)]
df14 <- merge(df_dist, df_error, by = "learning.condition")
colnames(df14) <- c("learning condition", "p-value distance improvement", "p-value errors improvement")
kable(df14, caption="Paired T test comparing individual performance improvement from block 1-4 in different conditions")
```
